The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-02-09 paper.tex
update

  \begin{equation}
     |\mathbf{B}(R, z)|=B_{0}\exp{-z/z_{0}}\exp{-R/R_{0}},
     \label{magnetic-field}
  \end{equation}

@@

  \Cref{fig_xray-map} is quite revealing in several ways.\
  First, the symmetric eROSITA bubbles can be formed by an inclined jet within a thin disk\
  of dense interstellar medium.\

@@

\section*{Data Availability}
The data underlying this article are available in the article and in its online supplementary material.

>>>>

  \begin{equation}
     |\mathbf{B}(R, z)|=B_{0}\exp\left[-\frac{z}{z_{0}}\right]\exp\left[-\frac{R}{R_{0}}\right],
     \label{magnetic-field}
  \end{equation}

@@

  \Cref{fig_xray-map} is quite revealing in several ways.\

  First, the broad agreement between simulated and observed X-ray map hint that\
  the symmetric eROSITA bubbles can be properly formed by an inclined jet within a thin disk\
  of dense interstellar medium.\

@@

The broad agreement between simulated and observed X-ray map provides supporting\
evidence for the inclined jet scenario,
\section*{Data Availability}
The data underlying this article are available in the article and in its online supplementary material.
